Changes in the justification of educational inequalities: The role of perceptions of inequality and meritocracy during the COVID pandemic

### 2024-03-25 paper.Rmd
arreglo footnote tab3

# table 3: interacciones
omit <- "(education)|(ess)|(quintil1)|(edad)|(sexo)|(pos_id)|(des_perc)"
texreg::texreg(list(educ6,educ3,educ1),
                custom.note = "\\item *** p < 0.001; ** p < 0.01; * p < 0.05.
Note: All the models are controlled by educational level, income quintile, subjective social status, age, gender, <br> political position and inequality perception",
                omit.coef = omit,
                include.loglik = FALSE,
                include.aic = FALSE,
                custom.coef.names = c("Intercept",
                                      "Wave",
                                      "Wave^2",
                                      "Merit: Talent",
                                      "Merit: Effort",
                                      "Wave * Merit: Talent",
                                      "Wave * Merit: Effort"
                                      ),
                custom.gof.names = c("BIC",
                                     "Num. obs.",
                                     "Num. groups: Individuals",
                                     "Var: Individuals (Intercept)",
                                     "Var: Residual",
                                     "Var: Individuals Wave",
                                     "Var: Individuals Merit: Talent",
                                     "Cov: Individuals (Intercept) Wave",
                                     "Cov: Individuals (Intercept) Merit: Talent",
                                     "Cov: Individuals Wave Merit: Talent",
                                     "Var: Individuals Merit: Effort",
                                     "Cov: Individuals (Intercept) Merit: Effort",
                                     "Cov: Individuals Wave Merit: Effort"),  
               caption = paste("(\\#tab:interact)","Interaction effects for the justification of economic inequality"),
               center = TRUE,
               caption.above = TRUE,
               scalebox = 0.765,
               float.pos = "!ht", 
               booktabs = TRUE, 
               use.packages = FALSE, 
               include.rs = FALSE, 
               include.rmse = FALSE,
               include.ci = FALSE,
               threeparttable = TRUE)
```

>>>>

# table 3: interacciones
omit <- "(education)|(ess)|(quintil1)|(edad)|(sexo)|(pos_id)|(des_perc)"
texreg::texreg(list(educ6,educ3,educ1),
                custom.note = "\\item *** p < 0.001; ** p < 0.01; * p < 0.05. Note: All the models are controlled by educational level, income quintile, subjective social status, age, gender, political position, and inequality perception",
                omit.coef = omit,
                include.loglik = FALSE,
                include.aic = FALSE,
                custom.coef.names = c("Intercept",
                                      "Wave",
                                      "Wave^2",
                                      "Merit: Talent",
                                      "Merit: Effort",
                                      "Wave * Merit: Talent",
                                      "Wave * Merit: Effort"
                                      ),
                custom.gof.names = c("BIC",
                                     "Num. obs.",
                                     "Num. groups: Individuals",
                                     "Var: Individuals (Intercept)",
                                     "Var: Residual",
                                     "Var: Individuals Wave",
                                     "Var: Individuals Merit: Talent",
                                     "Cov: Individuals (Intercept) Wave",
                                     "Cov: Individuals (Intercept) Merit: Talent",
                                     "Cov: Individuals Wave Merit: Talent",
                                     "Var: Individuals Merit: Effort",
                                     "Cov: Individuals (Intercept) Merit: Effort",
                                     "Cov: Individuals Wave Merit: Effort"),  
               caption = paste("(\\#tab:interact)","Interaction effects for the justification of economic inequality"),
               center = TRUE,
               caption.above = TRUE,
               scalebox = 0.765,
               float.pos = "!ht", 
               booktabs = TRUE, 
               use.packages = FALSE, 
               include.rs = FALSE, 
               include.rmse = FALSE,
               include.ci = FALSE,
               threeparttable = TRUE)
```
